### 2024-11-04 PaperSections.Rmd
Changes from committee meeting - Nov 1

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ng) Spring 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))
```

@@

# Spatial Comparison

## Fall 2J3KL

# Set up relationship data frame
lr_dat <- data.frame(year = unique(fishy_dat$year)[1:26], jkl_NLFPM_bm = rep$iye[1:26])

load(file = "./ModelSaves/3LFallCamp_Length.RData")

lr_dat$l_NLFPM_bm <- rep$iye

# Linear relationship 
fit <- lm(jkl_NLFPM_bm~l_NLFPM_bm, data = lr_dat)
cor.test(x = lr_dat$jkl_NLFPM_bm, y = lr_dat$l_NLFPM_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

## - Figure 4

```{r}
p18 <- ggplot(data = lr_dat, aes(x = l_NLFPM_bm, y = jkl_NLFPM_bm)) +
  geom_smooth(method = "lm", se = TRUE, color = "darkgrey") +
  geom_point(aes(colour = year), size = 1.5) +

  scale_x_continuous(name = "3L NLFPM Abundance Index", expand = c(0.005,0)) +
  scale_y_continuous(name = "2J3KL NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_colour_gradient2(name = "Year", limits = c(1995,2021), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
        legend.position = 'right', legend.direction = "vertical",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"))

ggsave(filename = "spatialcomp.tiff", device = "tiff", plot = p18, path = "./Figures",
       dpi = 300, width = 5, height = 4.5, units = "in")
```

>>>>

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("\nf) Spring 3L Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ng) Spring 3L Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))
```

@@
